On Secure Delegation of SampBQP with a Classical Client

### 2020-02-29 preliminaries.tex
Fix BQP definition

\begin{definition} [$\BQP$]
	\Ethan{TODO: Replace this with something that makes more sense}
	A language $L$ is in $\BQP$ if it can be decided by some uniform quantum circuit family.
\end{definition}

>>>>

\begin{definition} [$\BQP$]
	\Ethan{TODO: Replace this with something that makes more sense}
	$\SampBQP$ is the class of languages $L$ for which for all $n\in\bbN$ there exists a quantum circuit constructible in time $\poly(n)$ that, given any $x\in\set{0, 1}^n$ as input, correctly decides whether $x\in L$ at least $\frac{2}{3}$ of the time.
\end{definition}
